### 2025-01-14 article/article.tex
fix labels, fix problem with graphics path and suround with curly braces, start technical document

  \affiliation[upi]{organization={Department of Computer Science Education Universitas Pendidikan Indonesia},%Department and Organization
    addressline={Jl. Dr. Setiabudi No.229},
    postcode={40154},
    city={Bandung},
    country={Indonesia}}
  \begin{abstract}
    Numerical models of systems are a crucial part of science and engineering. The use of machine learning in this space for operator learning provides an alternative as data-driven surrogates. The Fourier Transform provides a key component for learning the relationship between a function and its derivatives. Building on Spectral Neural Operators (SNO), we propose a Support Vector Machine (SVM) based framework to learn the underlying governing equations of a system based on data. We study the viability and interpretability of the proposed framework on the derivative equation and the Burgers' equation. The model is able to learn from mathematically correct random data and is able to partially generalize to an exact solution of the Burgers' equation. The learned model is interpreted and verified to have learned the correct contributions of the input function coefficients to the output function coefficients.
  \end{abstract}
  \begin{keyword}
    %% keywords here, in the form: keyword \sep keyword
    Operator Learning \sep LSSVR \sep PDE
    % keyword one \sep keyword two
    %% PACS codes here, in the form: \PACS code \sep code
    % \PACS 0000 \sep 1111
    %% MSC codes here, in the form: \MSC code \sep code
    %% or \MSC[2008] code \sep code (2000 is the default)
    \MSC 35-04 \sep 68T99
  \end{keyword}

@@

@@

@@

The p-matrix shows the difference in contributions of both input functions. For the inviscid equation, the contributions mainly come from the forcing term. The current solution contributes a smaller amount in comparison. There is similarity with the antiderivative p-matrices in this case. The contributions to each output wave number mainly come from input coefficients with the same wave number. However, there is a noticeable contribution from other wave numbers too unlike the antiderivative case. The biggest contribution from the current solution is the constant/bias term. For higher viscosity values, notice that the contribution of the previous solution increases. The increase is more pronounced for higher frequencies. This aligns with the quadratic scaling from the wave number on the coefficients \citep{canutoSpectralMethodsEvolution2007}. The p-matrix for lower viscosity values show more structured contribution of other wave numbers in comparison to the higher wave numbers. This structure comes in the form of a grid pattern. For the real components of the output, the contribution of other wave numbers oscillate between higher and lower values depending on whether the input component is real or not. The imaginary output components on the other hand have a more constant contribution across the input components. The contribution once again become more pronounced the higher the absolute value of the wave number.
\section{Conclusion}
\noindent Based on the results of the research into \MakeLowercase{\judul}, several conclusions can be drawn.
\begin{enumerate}
  \item The proposed SpectralSVR model is able to learn the relationships defined by PDEs. This is done using a model that learns in the Fourier domain with Fourier Transforms and Inverse Transform bridging the Fourier domain and the physical domain.
  \item Interpretation of the proposed model can be done to a certain extent using two tools which are the correlation image and p-matrix developed by \citet{alisationInterpretationSupport2007}. This interpretation shows that the model correctly attributes the relationship of the input coefficients to the output coefficients.
  \item The proposed model is also capable in dealing with noise and partial data as shown in scenario 1.
        % \item The model's capabilities are also verified using exact solution. This revealed that for some configurations the model is able to successfully generalize to exact solutions.
\end{enumerate}

@@

Through these developments, the SpectralSVR model has the potential to not only refine its generalization capabilities, as evidenced by its partial success with exact solutions, but also to expand its utility across diverse and complex problems. These steps will contribute to advancing computational approaches for SciML-based modelling and establish the proposed framework as a versatile tool in this domain.
\bibliographystyle{elsarticle-harv}
\bibliography{references.bib}
\end{document}

>>>>

  \affiliation[upi]{organization={Department of Computer Science Education Universitas Pendidikan Indonesia},%Department and Organization
    addressline={Jl. Dr.\ Setiabudi No.229},
    postcode={40154},
    city={Bandung},
    country={Indonesia}}
  \begin{abstract}
    Numerical models of systems are a crucial part of science and engineering. The use of machine learning in this space for operator learning provides an alternative as data-driven surrogates. The Fourier Transform provides a key component for learning the relationship between a function and its derivatives. Building on Spectral Neural Operators (SNO), we propose a Support Vector Machine (SVM) based framework to learn the underlying governing equations of a system based on data. We study the viability and interpretability of the proposed framework on the derivative equation and the Burgers' equation. The model is able to learn from mathematically correct random data and is able to partially generalize to an exact solution of the Burgers' equation. The learned model is interpreted and verified to have learned the correct contributions of the input function coefficients to the output function coefficients.
  \end{abstract}
  \begin{keyword}
    %% keywords here, in the form: keyword \sep keyword
    Operator Learning \sep{} LSSVR \sep{} PDE
    % keyword one \sep keyword two
    %% PACS codes here, in the form: \PACS code \sep code
    % \PACS 0000 \sep 1111
    %% MSC codes here, in the form: \MSC code \sep code
    %% or \MSC[2008] code \sep code (2000 is the default)
    \MSC{} 35{-}04 \sep{} 68T99
  \end{keyword}

@@

To test the generalization capabilities of the model, we use the sine function with a period of one shown in \lccref{eq:sine_function}. The derivative is simply \lccref{eq:sine_derivative}. The functions are discretized and noise is added. Finally, the values go through the same transformations to become feature and target coefficients.
\begin{align}
  f(t) & = 2\pi \cos\left(2\pi t\right)\label{eq:sine_derivative} \\
  u(t) & = \sin\left(2\pi t\right)\label{eq:sine_function}
\end{align}

@@

To test the generalization capability of the model on other function families, we use an exact solution provided in the literature shown in \lccref{eq:burgers_exact_solution} \citep{woodExactSolutionBurgers2006,wazwazPartialDifferentialEquations2010,bentonTableSolutionsOnedimensional1972}.
\begin{equation}
  u(x,t) = \frac{2\nu\pi e^{-\pi^2\nu t}\sin(\pi x)}{a+e^{-\pi^2\nu t}\cos(\pi x)} \label{eq:burgers_exact_solution}
\end{equation}

@@

The p-matrix shows the difference in contributions of both input functions. For the inviscid equation, the contributions mainly come from the forcing term. The current solution contributes a smaller amount in comparison. There is similarity with the antiderivative p-matrices in this case. The contributions to each output wave number mainly come from input coefficients with the same wave number. However, there is a noticeable contribution from other wave numbers too unlike the antiderivative case. The biggest contribution from the current solution is the constant/bias term. For higher viscosity values, notice that the contribution of the previous solution increases. The increase is more pronounced for higher frequencies. This aligns with the quadratic scaling from the wave number on the coefficients \citep{canutoSpectralMethodsEvolution2007}. The p-matrix for lower viscosity values show more structured contribution of other wave numbers in comparison to the higher wave numbers. This structure comes in the form of a grid pattern. For the real components of the output, the contribution of other wave numbers oscillate between higher and lower values depending on whether the input component is real or not. The imaginary output components on the other hand have a more constant contribution across the input components. The contribution once again become more pronounced the higher the absolute value of the wave number.
\section{Conclusion}
\noindent Based on the results of the research into \MakeLowercase{\judul}, several conclusions can be drawn.
\begin{enumerate}
  \item The proposed SpectralSVR model is able to learn the relationships defined by PDEs. This is done using a model that learns in the Fourier domain with Fourier Transforms and Inverse Transform bridging the Fourier domain and the physical domain.
  \item Interpretation of the proposed model can be done to a certain extent using two tools which are the correlation image and p-matrix developed by \citet{ustunVisualisationInterpretationSupport2007}. This interpretation shows that the model correctly attributes the relationship of the input coefficients to the output coefficients.
  \item The proposed model is also capable in dealing with noise and partial data as shown in scenario 1.
        % \item The model's capabilities are also verified using exact solution. This revealed that for some configurations the model is able to successfully generalize to exact solutions.
\end{enumerate}

@@

Through these developments, the SpectralSVR model has the potential to not only refine its generalization capabilities, as evidenced by its partial success with exact solutions, but also to expand its utility across diverse and complex problems. These steps will contribute to advancing computational approaches for SciML-based modelling and establish the proposed framework as a versatile tool in this domain.

\input{apendix.tex}

\bibliographystyle{elsarticle-harv}
\bibliography{references.bib}
\end{document}

### 2025-01-14 skripsi/abstrak.tex
fix labels, fix problem with graphics path and suround with curly braces, start technical document

% !TEX root = ./skripsi.tex
\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{ABSTRAK}
\begin{center}
\textbf{\large  ABSTRAK}\\[0.5cm]
\textbf{\large Aproksimasi Solusi \textit{Govering Equations} dengan \emph{Fourier Transform} dan \textit{Support Vector Machine}}\\[0.5cm]
\textbf{Oleh}\\
\textbf{\penulis}\\
\textbf{NIM: \nim}\\[2em]
\end{center}

\noindent Model numerik sebuah sistem merupakan bagian penting dari ilmu pengetahuan dan \textit{engineering}. Penggunaan \textit{Machine Learning} (ML) dalam ruang ini untuk pembelajaran operator menyediakan alternatif sebagai \textit{data-driven surrogates}. \textit{Fourier Transform} menyediakan komponen kunci untuk mempelajari hubungan antara suatu fungsi dan turunannya. Berdasarkan \textit{Spectral Neural Operators (SNO)}, kami mengusulkan kerangka kerja berbasis \textit{Support Vector Machine (SVM)} untuk mempelajari persamaan dasar yang mengatur suatu sistem berdasarkan data. Kami mempelajari kelayakan dan interpretabilitas kerangka kerja yang diusulkan pada persamaan turunan dan persamaan Burgers. Model ini mampu belajar dari data acak yang secara matematis benar dan sebagian mampu melakukan generalisasi ke solusi eksak dari persamaan Burgers. Model yang dipelajari diinterpretasikan dan diverifikasi untuk mempelajari kontribusi yang benar dari koefisien fungsi masukan terhadap koefisien fungsi keluaran.
% \noindent Abstrak merupakan penjelasan singkat dan padat tentang pekerjaan dan hasil penelitian TA, yang dituliskan secara teknis. Abstrak memiliki karakter tegas dan komprehensif, dan hanya dapat dituliskan setelah pekerjaan penelitian telah mencapai tahap tertentu, dan karenanya ada hasil penelitian yang dapat dilaporkan. Abstrak ditulis menjelang akhir penyelesaian penulisan buku TA.

>>>>

% !TEX root = ./skripsi.tex
\clearpage
\phantomsection{}
\addcontentsline{toc}{chapter}{ABSTRAK}
\begin{center}
\textbf{\large  ABSTRAK}\\[0.5cm]
\textbf{\large Aproksimasi Solusi \textit{Govering Equations} dengan \emph{Fourier Transform} dan \textit{Support Vector Machine}}\\[0.5cm]
\textbf{Oleh}\\
\textbf{\penulis}\\
\textbf{NIM:\@\nim}\\[2em]
\end{center}

\noindent Model numerik sebuah sistem merupakan bagian penting dari ilmu pengetahuan dan \textit{engineering}. Penggunaan \textit{Machine Learning} (ML) dalam ruang ini untuk pembelajaran operator menyediakan alternatif sebagai \textit{data-driven surrogates}.\ \textit{Fourier Transform} menyediakan komponen kunci untuk mempelajari hubungan antara suatu fungsi dan turunannya. Berdasarkan \textit{Spectral Neural Operators (SNO)}, kami mengusulkan kerangka kerja berbasis \textit{Support Vector Machine (SVM)} untuk mempelajari persamaan dasar yang mengatur suatu sistem berdasarkan data. Kami mempelajari kelayakan dan interpretabilitas kerangka kerja yang diusulkan pada persamaan turunan dan persamaan Burgers. Model ini mampu belajar dari data acak yang secara matematis benar dan sebagian mampu melakukan generalisasi ke solusi eksak dari persamaan Burgers. Model yang dipelajari diinterpretasikan dan diverifikasi untuk mempelajari kontribusi yang benar dari koefisien fungsi masukan terhadap koefisien fungsi keluaran.
% \noindent Abstrak merupakan penjelasan singkat dan padat tentang pekerjaan dan hasil penelitian TA, yang dituliskan secara teknis. Abstrak memiliki karakter tegas dan komprehensif, dan hanya dapat dituliskan setelah pekerjaan penelitian telah mencapai tahap tertentu, dan karenanya ada hasil penelitian yang dapat dilaporkan. Abstrak ditulis menjelang akhir penyelesaian penulisan buku TA.
